Adaption of the Chumbley Score to matching of bullet striation marks

### 2018-03-07 doc/paper.Rmd
image relocation
corrected number

The majority of Bullet profiles and signatures of the Hamby study \citep{hamby} used in this paper are extracted by procedures mentioned by  \citet{aoas}. The scans for the Hamby study come from two sources namely, NIST scans \citep{nist} and scans produced at Iowa State University. Both scans were generated using confocal microscopes but at different resolutions. The NIST database contains scans of the bullet sets Hamby 44 and 252 with the resolution 1.5625 $\mu m$ per pixel. The Iowa State scans are available for only the Hamby 44 bullet set and at a resoultion of 0.065 $\mu m$ per pixel. The data used by \citet{chumbley, hadler} on the other hand, was produced by a profilometer at a resolution of about 0.73 $\mu m$ per pixel. The different resolutions indicate that the length of the digitized markings would be significantly different for each setting.

@@

The Chumbley score algorithm takes input as two vectorized processes.  Here the processes are of the form $z(t)$ which is a spatial process for some location indexed with $t$. This means that while $z(t)$ represents any striae, $z(t_1)$ is a realization of the spatial process. $t$ here denotes a vector of equally spaced pixel locations for the striation marks under consideration. The word 'pixel' refers to the resolution of the confocal light microscope. In the case for bullet signatures extracted from NIST ballistics database \citep{nist} of the Hamby study, a pixel corresponds to approximately 1.56 microns. The vectorized processes representing two sets of striaes are therefore shown as $x(t_1)$, $t_1 = 1,2,...T_1$ and $y(t_2)$, $t_2 = 1,2...T_2$. Here $x$ and $y$ denote two instances of the process $z(*)$ which means two striation marks, while the indexing $t$ or pixel range is shown as $t_1$ and $t_2$ for $x$ and $y$ respectively. This representation of $t$ as $t_1$ and $t_2$ lets us identify them as either of same or different lengths. The striation marks under consideration are potentially from two different bullets whose source needs to be identified as being same or different. $T_1$ and $T_2$, as represented above, are the final pixel indexes of each marking and therefore give the respective lengths of the markings. The similarity in the two markings is then judged by the algorithm on the basis of cross-correlation of a fixed and constant number consecutive pixels (say $k$) taken from the two markings. This can for example be $k$ taken from the two indexed marking $x(t_1)$ and $y(t_2)$ such that in theory $k$ remains smaller than length of the two striae or marks. Depending on what stage of the algorithm we are in, matching of different pixel lengths and locations is done. This in the end, effectively compares all possible windows that would guarantee in quantifying the two marks or striae as coming from the same source or not.

>>>>

The majority of Bullet profiles and signatures of the Hamby study \citep{hamby} used in this paper are extracted by procedures mentioned by  \citet{aoas}. The scans for the Hamby study come from two sources namely, NIST scans \citep{nist} and scans produced at Iowa State University. Both scans were generated using confocal microscopes but at different resolutions. The NIST database contains scans of the bullet sets Hamby 44 and 252 with the resolution 1.5625 $\mu m$ per pixel. The Iowa State scans are available for only the Hamby 44 bullet set and at a resoultion of 0.65 $\mu m$ per pixel. The data used by \citet{chumbley, hadler} on the other hand, was produced by a profilometer at a resolution of about 0.73 $\mu m$ per pixel. The different resolutions indicate that the length of the digitized markings would be significantly different for each setting.

@@

The Chumbley score algorithm takes input as two vectorized processes.  Here the processes are of the form $z(t)$ which is a spatial process for some location indexed with $t$. This means that while $z(t)$ represents any striae, $z(t_1)$ is a realization of the spatial process. $t$ here denotes a vector of equally spaced pixel locations for the striation marks under consideration. The vectorized processes representing two sets of striaes are therefore shown as $x(t_1)$, $t_1 = 1,2,...T_1$ and $y(t_2)$, $t_2 = 1,2...T_2$. Here $x$ and $y$ denote two instances of the process $z(*)$ which means two striation marks, while the indexing $t$ or pixel range is shown as $t_1$ and $t_2$ for $x$ and $y$ respectively. This representation of $t$ as $t_1$ and $t_2$ lets us identify them as either of same or different lengths. The striation marks under consideration are potentially from two different bullets whose source needs to be identified as being same or different. $T_1$ and $T_2$, as represented above, are the final pixel indexes of each marking and therefore give the respective lengths of the markings. The similarity in the two markings is then judged by the algorithm on the basis of cross-correlation of a fixed and constant number consecutive pixels (say $k$) taken from the two markings. This can for example be $k$ taken from the two indexed marking $x(t_1)$ and $y(t_2)$ such that in theory $k$ remains smaller than length of the two striae or marks. Depending on what stage of the algorithm we are in, matching of different pixel lengths and locations is done. This in the end, effectively compares all possible windows that would guarantee in quantifying the two marks or striae as coming from the same source or not.

<!-- The word 'pixel' refers to the resolution of the confocal light microscope. In the case for bullet signatures extracted from NIST ballistics database \citep{nist} of the Hamby study, a pixel corresponds to approximately 1.56 microns. -->
